---
title: "EDA"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Imports
```{r message=FALSE}
library(tidyverse)
library(lubridate)
library(GGally)
```

## Introduction
Exploratory data analysis for LV Datathon project.

## Read in data
```{r cars}
df <- read.csv("data/train.csv")

# Make column names consistent
cols <- colnames(df) %>%
  str_replace_all(fixed("."), "_")  %>%
  tolower()

cols[cols == "employmentstatus"] <- "employment_status"
colnames(df) <- cols

# Make variables with low number of unique values factors
df <- df %>%
  mutate(number_of_open_complaints = as.factor(number_of_open_complaints),
         number_of_policies = as.factor(number_of_policies))
```

Are there missing values?
```{r}
table(is.na(df))
```

## Target variable
Target variable is `total_claim_amount`:
```{r}
qplot(df$total_claim_amount, geom = "histogram", bins = 40)
```

Are there zero values?
```{r}
table(df$total_claim_amount == 0)
```

No but there is strangely small amounts. If this is pounds and these aren't mistakes then these are some real petty people:
```{r}
sum(df$total_claim_amount < 1)
```

## Predictor variables
### Continuous variables
```{r}
df %>%
  select_if(is.numeric) %>%
  ggpairs(aes(alpha = 0.2))
```

In terms of the correlation only two of the continuous variables seem to have a strong association with the `total_claim_amount`. These are `income` and `monthly_premium_auto`.
```{r}
df %>%
  select_if(is.numeric) %>%
  pivot_longer(-total_claim_amount, names_to = "feature", values_to = "X") %>%
  ggplot(aes(x = X, y = total_claim_amount)) +
  geom_point() +
  facet_wrap(~feature, scales = "free")
```
`months_since_last_claim` and `months_since_policy_inception` don't seem like they will be particularly useful features. I will drop them for now.
We can see that having no income seems to be important, this is captured by the `employment_status` variable.
```{r}
df <- df %>%
  select(-months_since_last_claim, -months_since_policy_inception)
```


```{r}
df %>%
  ggplot(aes(x = monthly_premium_auto, y = total_claim_amount,
             colour = location_code)) +
  geom_point()
```

I'm not sure exactly what is causing the weird structure in the plot above, but `location_code` separates it out extremely well. The top "segment" can be separated out using employment status.

```{r}
df %>%
  ggplot(aes(x = monthly_premium_auto, y = total_claim_amount,
             colour = employment_status)) +
  geom_point()
```


## Categorical variables
```{r}
df %>%
  select_if(is.character) %>%
  apply(2, {function(x) length(unique(x))})
```
Drop customer (all unique so likely not useful) and country (all US).
```{r}
df <- select(df, -customer, -country)
```

Look at effective to date see if that could be useful:
```{r}
df$effective_to_date <- as.Date(mdy(df$effective_to_date))

df %>%
  ggplot(aes(x=effective_to_date, y=total_claim_amount)) +
  geom_point()
```
Assume not informative:
```{r}
df <- select(df, -effective_to_date)
```

```{r}
df <- df %>%
  mutate_if(is.character, as.factor)

df %>%
  select_if(function(col) is.factor(col) | all(col == .$total_claim_amount)) %>%
  pivot_longer(-total_claim_amount) %>%
  ggplot(aes(x = value, y = total_claim_amount)) +
  geom_boxplot() +
  facet_wrap(~name, scales = "free", nrow = 3) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Bit cramped so will save it larger
ggsave("plots/boxplot.png", width = 10, height = 10)
```

`location_code` seems very informative. Below I drop a bunch of variables that don't look particularly informative:
```{r}
# These ones look ok to drop (if aiming for a simple model)
df <- df %>%
  select(-sales_channel, -state, -state_code, -vehicle_size)

# These ones are perhaps a bit more dubious. But for a simple first model might
# be worth dropping
df <- df %>%
  select(-claim_reason, -education, -number_of_policies, -policy, -policy_type,
         -response, -gender, -number_of_open_complaints)
```

Write out this simplified data set:
```{r}
write_csv(df, "data/train_simple.csv")
```







